Dynamic Adaptive Saturated Sliding Mode Control For Deployment of Tethered Satellite System

### 2016-11-04 manuscript.tex
20161104

From~(\ref{eq:varcon0}), it is easy to find that the boundedness of $\hat{\tau}_{t0}$ is different from $\hat{\tau}_\theta$'s and $\hat{\tau}_\phi$'s, since $\hat{\tau}_{t0}$ just owns the negative boundedness due to positive $\tau_t$. However, this issue doesn't conform to conventional hypotheses about input saturation, i.e., for adaptive sliding mode control law design, $\hat{\tau}_{t0}$ doesn't fulfil the requirement of transformation of limited inputs, leading to the nonrigorous stability analysis~\cite{Hu2008552,6060930}. To cope better with the missing positive boundedness, we initiatively introduce the dimensionless length $\lambda$ into the dimensionless tension to establish a reasonable positive boundedness, and hence general limited inputs are produced by the novel dimensionless transformations:

@@

where $\hat\bullet$ stands for the measurement of the term $\bullet$ with uncertainties, and $\bm\tau_d$ is the external disturbance meaning  space perturbations, such as gravity gradient torque, aerodynamic interference and solar radiation pressure torque. $\varpi$ is the uncertainty boundary parameter, and here we select $\varpi=2$. In this simulation, the measured terms can be specified as: $\hat{\bar m}=1.1\bar m$ may mean some space debris affixed to the subsatellite; $\bar L=1.02L$ and $\bar \Omega=0.98\Omega$ mean some measurement errors happening to the total length and the orbital angular velocity. In Fig~\ref{fig:6}, although the dynamics have been already stable, the tension is switching in the high frequency. It is commonplace in the sliding mode control law design, called chattering, since the signum function is used in the input, which may cause unmodelled high frequency dynamics, and for reducing the chattering, we introduce the boundary layer technique into the proposed control laws through replacing $sign(x)$ by $sat(x/\nu)$, where

>>>>

From~(\ref{eq:varcon0}), it is easy to find that the boundedness of $\hat{\tau}_{t0}$ is different from $\hat{\tau}_\theta$'s and $\hat{\tau}_\phi$'s, since $\hat{\tau}_{t0}$ just owns the negative boundedness due to positive $\tau_t$. However, this issue doesn't conform to conventional hypotheses about input saturation, i.e., for adaptive sliding mode control law design, $\hat{\tau}_{t0}$ doesn't fulfil the requirement of transformation of limited inputs, leading to the nonrigorous stability analysis~\cite{Hu2008552,6060930}. To cope better with the missing positive boundedness, we initiatively introduce the dimensionless length $\lambda$ into the dimensionless tension to establish a reasonable positive boundedness, and hence limited generalized inputs are produced by the novel dimensionless transformations:

@@

where $\hat\bullet$ stands for the measurement of the term $\bullet$ with uncertainties. $\varpi$ is the uncertainty boundary parameter, and here we select $\varpi=2$. $\bm\tau_d$ is the external disturbance meaning  space perturbations, such as gravity gradient torque, aerodynamic interference and solar radiation pressure torque.  In this simulation, the measured terms can be specified as: $\hat{\bar m}=1.1\bar m$ may mean some space debris affixed to the subsatellite; $\bar L=1.02L$ and $\bar \Omega=0.98\Omega$ mean some measurement errors happening to the total length and the orbital angular velocity. In Fig~\ref{fig:6}, although the dynamics have been already stable, the tension is switching in the high frequency. It is commonplace in the sliding mode control law design, called chattering, since the signum function is used in the input, which may cause unmodelled high frequency dynamics, and for reducing the chattering, we introduce the boundary layer technique into the proposed control laws through replacing $sign(x)$ by $sat(x/\nu)$, where
